Ae. albopictus CPP manuscript

### 2020-01-29 MS.Rmd
curves

```{r DI_plot, echo=FALSE, include=FALSE}
#plot with DI at 8 h shown as TWO DIFFERENT points (corresponding to two cabinets)
c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK")
DI_summary$pop<-factor(DI_summary$pop, levels=c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK"))
DI_plot<-ggplot(DI_summary, aes(x=pp, y=DI, group=pop)) + geom_point() + facet_wrap(~fct_reorder(pop, lat)) + theme_bw() + xlab("Photoperiod (hours)") + ylab("Dipause incidence")

@@

```{r CPP_calc_2018, echo=FALSE, include=FALSE}
#From Kevin Emerson
# the following fits the models of the given  using data from the
# data.frame d separately for the various treatments using a 5 parameter
# logistic model
d.model.fit <- drm(DI ~ pp, data = DI_summary, curveid = pop, fct = LL.5())
#plot(d.model.fit, log = "")
# output the parameters of the model fits:
summary(d.model.fit)
# estimate the 50% intercept
ED(d.model.fit, 50)
cpp_values<-data.frame(ED(d.model.fit, 50))
```

@@

>>>>

```{r DI_plot, echo=FALSE, include=FALSE}
#plot with DI at 8 h shown as TWO DIFFERENT points (corresponding to two cabinets)
c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK")
DI_summary$pop<-factor(DI_summary$pop, levels=c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK"))
DI_plot<-ggplot(DI_summary, aes(x=pp, y=DI, group=pop)) + geom_point() + facet_wrap(~fct_reorder(pop, lat)) + theme_bw() + xlab("Photoperiod (hours)") + ylab("Dipause incidence") 
```

@@

```{r CPP_calc_2018, echo=FALSE, include=FALSE}
#From Kevin Emerson
# the following fits the models of the given  using data from the
# data.frame d separately for the various treatments using a 5 parameter
# logistic model
d.model.fit <- drm(DI ~ pp, data = DI_summary, curveid = pop, fct = LL.5())
#plot(d.model.fit, log = "")
# output the parameters of the model fits:
summary(d.model.fit)
# estimate the 50% intercept
ED(d.model.fit, 50)
cpp_values<-data.frame(ED(d.model.fit, 50))

pm<-drc:::predict.drc(d.model.fit, type="response")
```

@@

```{r}
#Dose response curve plot from Jen
cpp<-read.table("CPP.csv", header=TRUE, sep=",")
cpp

fm1<-cbind(hatched, nothatched)~photoperiod
cppmodel<-glm(fm1, data=cpp, family=binomial())

summary(cppmodel)

fitteddata1<-predict(cppmodel,type="response")
fitteddata1

plot(cpp$photoperiod, fitteddata1, ylab="Probability of hatching",
     xlab="photoperiod", ylim=c(0,1))
     lines(cpp$photoperiod,fitteddata1, lty=1)
y<-cpp$hatched/(cpp$hatched+cpp$nothatched)
text(cpp$photoperiod,y)
hours<-
-(cppmodel$coefficients["(Intercept)"])/cppmodel$coefficients["photoperiod"]
hours
